---
title: "Markup & Markdown"
pagetitle: "Markup & Markdown"
---

```{r echo=FALSE}
knitr::read_chunk("./scripts/workshop_files.R")
```

## Description

This workshop will briefly introduce:

* markup languages used for communicating structure, style, and data.
* common applications of specific markup languages.
* converting between markup languages.

## Objectives

* Introduce a set of commonly used markup languages for authoring academic and web based content.
* Review markup in relation to communicating document structure, document styling, and machine interpretable data.
* Explore document content vs document presentation.

## Outcomes

* Articulate the differences between Markdown, html, xml, and LaTeX.
* Write a basic document in each of html and LaTeX.
* Convert documents between markup languages using a command line tool, Pandoc.

## What you will need

* A computer. Neither a tablet nor cell phone will suffice.

## Pre-load

* Set up an [Overleaf account](https://www.overleaf.com/)
* Install [Atom](https://atom.io/)
* Install [Pandoc](https://pandoc.org/installing.html). Just use the button prompt at the top, don't worry about all the extra text.

## Files

```{r loadfiles, results='asis', echo=FALSE}
```
